Reconstructing Propositional Proofs in Type Theory

### 2017-10-26 paper/sections/proof-reconstruction.tex
strip equations.
[ paper ] minor changes.

In the remainder part of this section, a formal description using
type theory is presented to build definitions and theorems of
functions necessary to emulate \Metis' inference rules.

@@

\begin{verbatim}
fof(p3, (r | ~ p), inf(conjunct, [p1])).
\end{verbatim}

>>>>

In the remainder part of this section, a formal description using
type theory is presented to build definitions and theorems of
functions necessary to reconstruct \Metis' inference rules.

@@

\begin{verbatim}
fof(p3, (r ∨ ¬ p), inf(conjunct, [p1])).
\end{verbatim}
